---
title: "ALodico-HW2"
author: "ASL"
date: "10/3/2019"
output: html_document
---
#test update commit
#read.me file
#git commit and push process here
#line 

Each Map will include:

#    A Basemap
# check    One map with a layer of points - Students may use either circles or markers
# check    One map with a layer of lines
#    One map with a layer of polygons
#    One of the maps must contain a variable which changes of the color of the elements or the marker with an accompanying legend
#    One map must contain a functioning layersControl() with two basemaps and two different layers (by name do not need to be a different type of layer)



```{r setup, include=FALSE}
library(leaflet)
library(rgdal)
##line file for Pgh Bridges
bridges <- readOGR("https://data.wprdc.org/dataset/d6e6c012-45f0-4e13-ab3b-9458fd56ad96/resource/c972b2cc-8396-4cd0-80d6-3051497da903/download/bridges_img.geojson")
smarttrash <- readOGR("https://data.wprdc.org/dataset/b1282e47-6a70-4f18-98df-f081e7406e34/resource/5c7edf21-421c-40ec-b851-d55aa5b3585f/download/smart_trash_containers.geojson")
#line file for Port Authority routes
#crs <- leafletCRS()
#PATlines <- readOGR(dsn = "C:/Users/TonyatCMU/Desktop/R4Ops/ALodico-HW2/PAAC_Routes_1903final" 
#                    , layer = "PAAC_Routes_1903final" 
                    # , GDAL1_integer64_policy = TRUE
#                    )
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown



```{r}
#point map
mp <- leaflet() %>%
  addTiles() %>%
  addMarkers(data = smarttrash)
mp
#trashy
```

## The Line file


```{r}
ml <- leaflet() %>%
  addTiles() %>%
  addPolylines(data = bridges)
ml

```

```{}


```
