---
title: "ALodico-HW2"
author: "ASL"
date: "10/3/2019"
output: html_document
---
#push commit seems to not be working. Instead, update file,
#go to the folder in github/hw2, and drag and drop into desktop
#version of github in the hw2-ALodico folder, Alodico-HW2 subforlder, 
#then click on upload files. Drag and drop this file into there.


# check    Each Map will include:A Basemap
# check    One map with a layer of points - Students may use either circles or markers
# check    One map with a layer of lines
# check    One map with a layer of polygons
# checks   One of the maps must contain a variable which changes of the color of the elements or the marker with an accompanying legend
# checkss  One map must contain a functioning layersControl() with two basemaps and two different layers (by name do not need to be a different type of layer)



```{r setup, include=FALSE}
library(leaflet)
library(rgdal)

#reading in all the files for the 
#mostly points for the first map (greenways are polygons, bridges are lines)
greenways <- readOGR("http://pghgis-pittsburghpa.opendata.arcgis.com/datasets/d6cb53f628eb49e2991f51b07ff32bad_0.geojson")
ballfields <- readOGR("http://pghgis-pittsburghpa.opendata.arcgis.com/datasets/87f3b2bdfa6646319a56e86521480efd_0.geojson")
playgrounds <- readOGR("https://data.wprdc.org/dataset/4b9c5947-5645-4dbc-a7b6-eb323418fe02/resource/eb0cf52f-3da1-4b77-8f6d-891dff8adfa0/download/playgroundequipment_img.geojson")
##point files for Pgh disposal sites and smart trash cans.
trash2 <- readOGR("https://data.wprdc.org/dataset/10dd50cf-bf29-4268-83e2-debcacea7885/resource/cdb6c800-3213-4190-8d39-495e36300263/download/wasterecovery_img.geojson")
trash <- readOGR("https://data.wprdc.org/dataset/b1282e47-6a70-4f18-98df-f081e7406e34/resource/5c7edf21-421c-40ec-b851-d55aa5b3585f/download/smart_trash_containers.geojson")
bridges <- readOGR("https://data.wprdc.org/dataset/d6e6c012-45f0-4e13-ab3b-9458fd56ad96/resource/c972b2cc-8396-4cd0-80d6-3051497da903/download/bridges_img.geojson")


#polygon files for wards and precincts

wards <- readOGR("http://pghgis-pittsburghpa.opendata.arcgis.com/datasets/dff605f73fe24791875567f1d942275d_0.geojson")
precincts <- readOGR("http://openac-alcogis.opendata.arcgis.com/datasets/faaf42d7eaa041cb9fa623ac7b42f475_0.geojson")
#2016 general election data
general16 <- read.csv("https://data.wprdc.org/dataset/ea85f4b5-0b95-41b8-86ee-f1e6d16fc409/resource/3e8b23b7-aa71-4850-9379-bce87f73d684/download/2016-general-election-results-by-precinct.csv")
```


## R Markdown



```{r}
#point map
#start with default basemap, then add satelite view, a black and white (AKA printer friendly) view, and a topographical basemap, AKA wrinkled. 
#From there, I added some points and polygons of some of the places you should put trash and places you shouldnt put trash. I had to take out one of the trash groups because it was for the county, and messed up the map zoom. 
mp <- leaflet() %>%
  addProviderTiles(providers$Hydda.Full, group = "Default") %>%
  addProviderTiles(providers$Esri.WorldImagery, group = "Satellite View") %>%
  addProviderTiles(providers$CartoDB.Positron, group = "Printer Friendly") %>%
  addProviderTiles(providers$Stamen.TopOSMRelief, group = "Wrinkled") %>%
  addCircles(data = trash, group = "Put trash here", color = "magenta", weight = 2) %>%
  addPolygons(data = greenways, group = "Don't leave trash here", color = "green")  %>%
  addCircles(data = ballfields, group = "Don't leave trash here", color = "lawngreen", weight = 6)  %>%
  addCircles(data = playgrounds, group = "Don't leave trash here", color = "chartreuse", weight = 4)  %>%
  addPolylines(data = bridges, group = "Definitely don't toss trash off these", color = "yellow", weight = 8) %>%
#this creates the box that lets you toggle the basemap and grouped layers
  addLayersControl(
    baseGroups = c("Default", "Satellite View", "Printer Friendly", "Wrinkled"),
    overlayGroups = c("Put trash here", "Dont leave trash here", "Definitely don't toss trash off these"),
#this keeps the box from being a pop out
    options = layersControlOptions(collapsed = FALSE)
  )
#this prints the map
mp
#trashy
```

## The Line Map


```{r}
# a simple map of Pittsburgh Bridges. Its also in the first map, bu I wasnt sure if you wanted each type of tile to have a map, so I left this one here. I had to change that awful default map though
ml <- leaflet() %>%
  addProviderTiles(providers$Hydda.Full) %>%
  addPolylines(data = bridges, color = "black")
ml

```

```{r}
#filtering the data here for the total # of votes. 
gen16total <- general16 %>%
  filter(Contest.Title == "BALLOTS CAST - TOTAL")
#joining the precincts to the voter data for the choropleth
precinctvotes <- geo_join(precincts, gen16total, "Muni_War_1", "Precinct.Name")

#bins for the choropleth, autogenerated ones were too uneven a distribution, and I was having trouble making dynamic ones that I could coerce into a list
bins <- c(0,200,300,400,500,600,800,1000,2000)
# I try to make the color gradient a bit pretty
pal <- colorBin("YlOrRd", domain = precinctvotes$Votes, bins = bins)

ms <- leaflet() %>%
#base layer
  addProviderTiles(providers$Wikimedia) %>%
#choropleth layer, thin lines for the borders, not full opacity so you can see the streets behind the colors
  addPolygons(data = precinctvotes,
              fillColor = ~pal(precinctvotes$Votes),
              fillOpacity = 0.75,
              weight = 1) %>%
# basic legend that shows the choropleth color bin ranges
  addLegend(pal = pal, 
              values = precinctvotes$Votes, 
              position = "bottomright", 
              title = "2016 Total votes by precinct")
# print it out
ms
#I want to come back to this one & do other election maps, but this is a decent start

```
